### 2018-12-30 writing/thesis/chapters/results.tex
Update convergence.

\chapter{Results}\label{chap:results}
\section{Convergence Test}
\begin{table}[htb]
  \centering
\caption{Numerical order of convergence of ADER-DG method}%
\label{tab:convergence-order}
\begin{tabular}{@{}lS[table-format=1.2]S[table-format=1.2]S[table-format=1.2]@{}}
\toprule
{Order} & {$L_1$} & {$L_2$} & {$L_\infty$}\\ \midrule
1 & 2.03 & 2.00 & 1.92\\
2 & 2.56 & 2.55 & 2.56\\
3 & 3.44 & 3.41 & 3.42\\
4 & 4.27 & 4.27 & 4.33\\
5 & 5.36 & 5.32 & 5.26\\
6 & 5.38 & 5.35 & 5.17\\
\bottomrule
\end{tabular}
\end{table}
\newcommand{\error}{\operatorname{Total-Error}}

@@

\section{Accurate CFD}
\section{Accurate Clouds}
\section{AMR Efficiency}
\section{Reactive Euler \textit{\&} Navier Stokes}

>>>>

\chapter{Results}\label{chap:results}
\section{Convergence Test}
\begin{table}[htb]
  \centering
\caption{Numerical order of convergence of ADER-DG method}%
\label{tab:convergence-order}
\begin{tabular}{@{}lS[table-format=1.2]S[table-format=1.2]S[table-format=1.2]@{}}
\toprule
{Order} & {$L_1$} & {$L_2$} & {$L_\infty$}\\ \midrule
1 & 2.03 & 2.00 & 1.92\\
2 & 2.56 & 2.55 & 2.55\\
3 & 3.43 & 3.40 & 3.44\\
4 & 4.44 & 4.44 & 4.67\\
5 & 5.37 & 5.34 & 5.28\\
6 & 5.43 & 5.42 & 5.30\\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}[htb]
  \centering
  \includegraphics{thesis_convergence}
  \caption{$L_2$-Error vs.\ Grid Size}
  \label{fig:convergence-l2-error}
\end{figure}

\newcommand{\error}{\operatorname{Total-Error}}

@@

\section{Accurate CFD}
\section{Accurate Clouds}
\section{AMR Efficiency}
To show the effectiveness of the \amr{}, we compare the time to solution of a simulation using \amr{} and another simulation with a fully refined mesh.
In detail, we compare
\begin{description}
\item[AMR] We use a coarse mesh with just $9 \times 9$ cells.
  Each cell can be refined up to three times.
  That is, the cells have sidelengths of roughly $\left( \SI{111.1}{\m}, \SI{37.04}{\m}, \SI{12.35}{\m} \right)$.
  As refinement thresholds we use $T_\text{refine} = 2.5$ and $T_\text{delete} = -0.5$ in \cref{eq:refinement-criterion}.
\item[Fine] We use a uniform grid where all cells have a sidelength corresponding to the finest mesh of the \amr{}-test case.
  In addition, we disable the reduction of global observables.
\end{description}
We use an \aderdg{}-method of order $4$ and thus have a minimal effective resolution of ca.\ $\SI{3.09}{\m}$.

To ensure a fair comparison, we ran both configurations with the same optimisation option.

We use a single node of the Haswell-nodes of the Supermuc (Phase 2).
The node has two xxx \textsc{cpu}s with 28 cores each.
We use the \tbb{} parallelisation of \exahype{}.
To find a reasonable parameter for the number of background threads, we ran a grid search.
We ran three \arm{} testcases for a simulation time of $\SI{1}{\min}$.
The best median performance was achieved by only using two background threads!

\section{Reactive Euler \textit{\&} Navier Stokes}
